MLH1 Data Report

### 2018-06-11 Main_Report.rmd
knitted batch12 data, fixed some bugs

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
### to integrate 'pass'/fail
### this should be in setup data

#quant_status (this isn't saving)
#for(i in 1:length(MLH1_data$mouse)){
#  MLH1_data$quant_status[i] <- ifelse( is.element(MLH1_data$mouse[i], pass_mice), "pass", NA)
#}

#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7,14,16,22) ]
#7: PERC male, 12: KAZ female! (14:CAST female, fake data) 16:HMI female

@@

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(data = df_list[[h]], y= adj_nMLH1.foci, x= quality, aes(colour = factor(Batch)), width = 0.25)
  # +   geom_rect(data = df_list[[h]], aes(fill=as.factor(quant_status)), alpha=0.5)

  + geom_jitter()
  + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") + scale_fill_manual(values=c(NA, "red"), breaks=NULL)

>>>>

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=TRUE}
### to integrate 'pass'/fail
### this should be in setup data

#quant_status (this isn't saving)
for(i in 1:length(MLH1_data$mouse)){
  MLH1_data$quant_status[i] <- ifelse( is.element(MLH1_data$mouse[i], pass_mice), "pass", NA)
}

#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7,16,22) ]

#7: PERC male, (14:CAST female, fake data) 16:HMI female, 22 other
#

@@

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(data = df_list[[h]], aes(colour = factor(Batch)), width = 0.25)+ geom_jitter(aes(y= adj_nMLH1.foci, x= quality))
  # +   geom_rect(data = df_list[[h]], aes(fill=as.factor(quant_status)), alpha=0.5)
#  + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") +scale_fill_manual(values=c(NA, "red"), breaks=NULL)
